\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-05-26 doc/paper.tex
no hashes in latex section

>>>>

\section{Type 2 errors: CS1 vs CS2}

\autoref{type2} gives an overview of type 2 error rates of methods CS1 and CS2 for different significance levels $\alpha$. Method CS2 is outperforming CS1 significantly in every instance.

{\centering \includegraphics[width=0.9\textwidth]{figures/type2-1}

\caption{Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error.}\label{fig:type2}
\end{figure}
